A Causal Model of \hbox{DBMS} Suboptimality\\

### 2017-08-08 subopt-tods17/cover-letter.tex
subopt tods submission

\begin{flushleft}
{\large\bf Young-Kyoon Suh}
\end{flushleft}
\medskip\hrule height 1pt
%\begin{flushright}
%\hfill Department of Computer Science, The University of Arizona, Tucson, AZ 85721 USA\\
%\hfill Tel: +1-520-370-1865
%(Please understand we cannot reveal our affiliation, as the manuscript should be double-blind.)
%\end{flushright} 
\begin{flushright}
\hfill National Institute of Supercomputing and Networking, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Korea Institute of Science and Technology Information (KISTI), 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Republic of Korea, 34141, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Tel: +82-42-869-0725
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Email: yksuh@kisti.re.kr
\end{flushright} 
%\vfill % forces letterhead to top of page

@@

\opening{Dear Prof. Christian S. Jensen:}

@@

\item No version of this manuscript has been previously published nor be currently under consideration for publication elsewhere. 
We have anonymized the current submission as directed by the double-blind
review guidelines on the TODS web site. Note that Section 9 (on pages 36--37) of
this manuscript summarizes the contributions in an attempt to draw 
a causal explanation of suboptimality and to uncover a fundamental limit 
on the number of operators that a DBMS may be able to support.

>>>>

\begin{flushleft}
{\large\bf Young-Kyoon Suh}
\end{flushleft}
\medskip\hrule height 1pt
%\begin{flushright}
%\hfill Department of Computer Science, The University of Arizona, Tucson, AZ 85721 USA\\
%\hfill Tel: +1-520-370-1865
%(Please understand we cannot reveal our affiliation, as the manuscript should be double-blind.)
%\end{flushright} 
\begin{flushright}
\hfill National Institute of Supercomputing and Networking
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Korea Institute of Science and Technology Information (KISTI)
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Republic of Korea, 34141
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Tel: +82-42-869-0725
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Email: {\tt yksuh@kisti.re.kr}
\end{flushright} 
%\vfill % forces letterhead to top of page

@@

\opening{Dear Prof.~Jensen:}

@@

\item No version of this manuscript has been previously published nor is
  currently under consideration for publication elsewhere.

\item We have anonymized the current submission as directed by the double-blind
review guidelines on the TODS web site. 
%Note that Section 9 (on pages 36--37) of
%this manuscript summarizes the contributions in an attempt to draw 
%a causal explanation of suboptimality and to uncover a fundamental limit 
%on the number of operators that a DBMS may be able to support.
